\bf Hierarchical Forecasts Reconciliation

### 2019-07-03 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
tidy up

	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.  Also notable by its absence in the above definition is any reference to {\em aggregation}. In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot easily be depicted in a similar fashion to Figure~\ref{fig:basichier} and or do not involve aggregation. {\bf Include brief summary of all non-traditional hierarchies - e.g. grouped hierarchies, temporal hierarchies with wierd overlapping, problems where we look at differences between variables etc.}  Finally, although the Definition~\ref{def:cohspace} makes clear reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.

@@

	As discussed in the previous section, for a number of reasons, coherence is not guaranteed when forecasts are produced for all series.  To ensure aligned decision making, it is desirable to adjust forecasts ex post to ensure coherence.  This process is referred to as {\em reconciliation}.  In the most general terms, reconciliation can be defined as follows

@@

	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.  One way to achieve this is with a matrix $\bm{SG}$, where $\bm{G}$ is an $(n-m)\times n$ matrix  (with some authors using $\bm{P}$ used in place of $\bm{G}$).  This facilitates an interpretation of reconciliation as a two-step process, in the first step, base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.

@@

	We begin by considering the special case of an orthogonal projection whereby $\bm{G}=\left(\bm{S}'\bm{S}\right)^{-1}\bm{S}'$.  This is equivalent to so called OLS reconciliation as introduced by \cite{Hyndman2011} where the connection between OLS and orthogonal projection should be clear.

@@

	In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.  The  first is that reconciliation should adjust the base forecasts as little as possible, i.e. the base and reconciled forecast should be `close'.  The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the truth.

	To address the first of these properties we make the concept of closeness more concrete, by considering the Euclidean distance between the base forecast $\hat{\bm{y}}$ and the reconciled forecast  $\tilde{\bm{y}}$.  A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ will be as small as possible while still ensuring that $\tilde{\bm{y}}\in\mathfrak{s}$.  In this sense reconciliation via orthogonal projection does leads to the smallest possible adjustments of the base forecasts.

@@

	\begin{theo}[Distance reducing property]\label{th:distred}
		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
		\begin{equation}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2.
		\end{equation}
	\end{theo}
	\begin{proof}
		Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ whenever $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$. Therefore,
		\begin{align}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
		&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
		\end{align}
		The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators \citep{Hun2001}, therefore
		\begin{equation*}
		\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le
		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
		\end{equation*}
	\end{proof}
	The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.

@@

	In particular, this measure is the

>>>>

	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.  Also notable by its absence in the above definition is any reference to {\em aggregation}. In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot easily be depicted in a similar fashion to Figure~\ref{fig:basichier} and or do not involve aggregation. {\bf Include brief summary of all non-traditional hierarchies - e.g. grouped hierarchies, temporal hierarchies with wierd overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes clear reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.

@@

	As discussed in the previous section, coherence is not guaranteed for a number of reasons.  To ensure aligned decision making, it is desirable to adjust forecasts ex post to ensure coherence.  This process is referred to as {\em reconciliation}.  In the most general terms, reconciliation can be defined as follows

@@

	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.  One way to achieve this is with a matrix $\bm{SG}$, where $\bm{G}$ is an $(n-m)\times n$ matrix  (some authors use $\bm{P}$ used in place of $\bm{G}$).  This facilitates an interpretation of reconciliation as a two-step process, in the first step, base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.

@@

	We begin by considering the special case of an orthogonal projection whereby $\bm{G}=\left(\bm{S}'\bm{S}\right)^{-1}\bm{S}'$.  This is equivalent to so called OLS reconciliation as introduced by \cite{Hyndman2011}.  We refrain from any discussion of regression models focusing instead on geometric interpretations.  However the connection between OLS and orthogonal projection should be clear, in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection of the data onto the span of the regressors.

@@

	In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.  The  first is that reconciliation should adjust the base forecasts as little as possible, i.e. the base and reconciled forecast should be `close'.  The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realisation that is the target of the forecast.

	To address the first of these properties we make the concept of closeness more concrete, by considering the Euclidean distance between the base forecast $\hat{\bm{y}}$ and the reconciled forecast  $\tilde{\bm{y}}$.  A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ will be as small as possible while still ensuring that $\tilde{\bm{y}}\in\mathfrak{s}$.  In this sense reconciliation via orthogonal projection leads to the smallest possible adjustments of the base forecasts.

@@

	\begin{theo}[Distance reducing property]\label{th:distred}
		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
		\begin{equation}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2.
		\end{equation}
	\end{theo}
	\begin{proof}
		Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ since $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$. Therefore,
		\begin{align}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
		&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
		\end{align}
		The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators \citep{Hun2001}, therefore
		\begin{equation*}
		\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le
		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
		\end{equation*}
	\end{proof}
	The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.

@@
